%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large\boldsymbol{ Aghapy Elgohary}}\\
  \text{Undergraduate Software Engineer }\\

  \textbf{Mobile : +02-0111-812-9621 } \\
  \textbf{ Email : aghapygad336@gmail.com } \\
  \href{https://www.linkedin.com/in/aghapy-mikhail-91a57718a/}{ LinkedIn : www.linkedin.com/aghapy-el-gohary}\\
  \href{https://github.com/aghapygad336}{\github Github :https://github.com/aghapygad336}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Faculty Of Engineering Alexandria University }{Alexandria, Egypt}
      { Computer and Communication Department.  }{Sep. 2016 -- June 2021}
      




%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \item{\textbf{\boldsymbol{8 Puzzle :}}}
      {a java application to solve the 8-Puzzle game using different search techniques like : Breadth Frist Search, Depth Frist Search and A*.}
    \item{\textbf{Image segmentation  :}}
      {Image segmentation is the classification of an image into different groups. There are different methods and one of the most popular methods is k-means clustering algorithm. K -means clustering , Normalized Cut algorithm is an unsupervised algorithm and it is used to segment the interest area from the background. Accuracy Measuring by F score algorithm}
    \item{\textbf{Face-Recognition :}}
      { face recognition with complete implementation in python of LDA & PCA  algorithm for the classification of the input labeled images and the goal performing in an acceptable way giving a best recognition accuracy of 95/100 used Non Face data accuracy was very bad because data wasn't Consistent.}
    \item{\textbf{Paint :}}
      {Applied OOP concepts using java , offer a big number of features that includes but is not limited to:
Drawing, Coloring, and Resizing.} 
\item{\textbf{Spelling System :}}
      {In this assignment i was  required to implement a binary search tree Initially
 will be given a dictionary of words to build my binary search tree ,the comparison between
strings .
.}\item{\textbf{The MENA Terrorism  :}}
      {The Global Terrorism Database  in ME-NA  terrorist attacks that occurred worldwide since 1970 Classification due to number of the top groups used different classifiers and measured  accuracy, precision, recall and F-measure as a of  models as Decision trees , Adaboost , k-nearest-neighbour .}\item{\textbf{Beach Resort :}}
      {Implemented using ReactJs For Rooms Services Menu.}
      \item{\textbf{Multithreading Application :}}
      {This project is about implementing 2 multi-threaded applications using the POSIX threads library in C to create and join threads. The first application is Matrix Multiplication  And then the rest of the execution consists of the merge algorithm .}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{\textbf{Languages : }}{
     {Python, Java, C, JavaScript, MATLAB, SQL}
   }
   \item{\textbf{Web Development: : }} {ReactJS, NodeJS,}
   \item{\textbf{Deep Learning : }} {TensorFlow, Keras}
   
   \item{\textbf{Other Tools/Frameworks : }} { OpenCV, GitHub,Colab, jupyter, Visual Studio,Linux}
   
   
 \resumeSubHeadingListEnd
 \section{Related Courses}
   

  \textbf {Object Oriented Programming}\hfill
  \textbf{Data-structures }\hfill
 \textbf{ Artificial Intelligence }\hfill\\
  \textbf {Database Management Systems}\hfill
  \textbf {Pattern Recognition}\hfill
  \textbf {Operating Systems}\hfill

   
   
 \resumeSubHeadingListEnd
 
 


%-------------------------------------------
\end{document}